---
title: "Data cleaning before Z-score generation"
output:
  html_notebook: default
  word_document: default
---
Authors: 
Serena Verdi

Adapted to QMIN-MC sample by candidate HZWC3
This script cleans and identifies suitable participants from raw files containing crucial information on QMIN-MC participants including:
- Demographics 
- MRI scans 
- Clinical scores 

Once suitable participants are identified, they are sub-divided into 2 data sets based on their diagnosis following the below criteria:
- Adaptation data set (df_a) - Healthy, Functional/Attentional Memory Symptoms 
- Test data set (df_t) - Any subtype of dementia

These data sets will then be utilised on the PCN Python code which generates normative models using a Bayesian regression hierarchical framework. 

#----------------------------------------------           
## - - - Set up - - -
#----------------------------------------------
# Import libraries
```{r setup}
library(data.table)
library(e1071)
library(dplyr)
library(tidyr)
library(stringr)
library(readr) #use readr package to ensure no corruption upon reading (as - can convert to .)
```
#Clear work space
```{r}
rm(list = ls())
```
#----------------------------------------------
## - - - Prepare data  - - -
#----------------------------------------------
# Import FreeSurfer data (adapt if have timpoint data etc)
#Load each sites data (individual files, combine them as site 1 and site 2, then merge them with site 2 files to create df1) From df1, generate the code to create a table with RIDs present in demographics, diagnosis, sessions and diagnosis amended. So create diagnosis amended from diagnosis. Gather a list of RIDs not present in all 4 files, then 
```{r}
# Cortical thickness data at both timepoints (1&2)
ct_1_lh <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/CUH Site 1/aparc_stats_thickness_lh.csv")

ct_1_rh <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/CUH Site 1/aparc_stats_thickness_rh.csv")

ct_2_lh <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/CPFT Site 2/aparc_stats_thickness_lh.csv")
  
ct_2_rh <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/CPFT Site 2/aparc_stats_thickness_rh.csv")

# Subcortical volume data at both timepoints (1&2)
sv_1 <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/CUH Site 1/subcortical_vol.csv")
sv_2 <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/CPFT Site 2/subcortical_vol.csv")

# Template data for copying the format of input data for the normative model
template <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/Template/Template.csv") 

# Demographic data which is needed for the input data for the normative model
demographics <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Demographics/Demographics.csv")
sessions <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Demographics/Sessions.csv")
clinicalscores <- read_csv("//Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Demographics/Clinical Scores.csv")
diagnosis <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Demographics/Diagnosis.csv")
```
#rename 'subject' to 'RID' (optional)
```{r}
ct_1_lh <- ct_1_lh %>% dplyr::rename("RID" = "lh.aparc.a2009s.thickness")
ct_1_rh <- ct_1_rh %>% dplyr::rename("RID" = "rh.aparc.a2009s.thickness")
ct_2_lh <- ct_2_lh %>% dplyr::rename("RID" = "lh.aparc.a2009s.thickness")
ct_2_rh <- ct_2_rh %>% dplyr::rename("RID" = "rh.aparc.a2009s.thickness")
sv_1 <- sv_1 %>% dplyr::rename("RID" = "Measure:volume")
sv_2 <- sv_2 %>% dplyr::rename("RID" = "Measure:volume")
```
# shorten RID to include just the id needed (optional)
```{r}
ct_1_lh$RID <- gsub("^\\.\\/sub\\-(\\d+)_ses\\-\\d+$", "\\1", ct_1_lh$RID)
ct_1_rh$RID <- gsub("^\\.\\/sub\\-(\\d+)_ses\\-\\d+$", "\\1", ct_1_rh$RID)
ct_2_lh$RID <- gsub("^\\.\\/sub\\-(\\d+)_ses\\-\\d+$", "\\1", ct_2_lh$RID)
ct_2_rh$RID <- gsub("^\\.\\/sub\\-(\\d+)_ses\\-\\d+$", "\\1", ct_2_rh$RID)

sv_1$RID <- gsub("^\\.\\/sub\\-(\\d+)_ses\\-\\d+$", "\\1", sv_1$RID)
sv_2$RID <- gsub("^\\.\\/sub\\-(\\d+)_ses\\-\\d+$", "\\1", sv_2$RID)

```
#Merge cortical thickness together
```{r}
ct1 <- merge(ct_1_lh, ct_1_rh, by = "RID", all.x = TRUE)
ct2 <- merge(ct_2_lh, ct_2_rh, by = "RID", all.x = TRUE)
# Concatenate ct1 and ct2 vertically
ct_combined <- bind_rows(ct1, ct2)
```
#Merge subcortical volumes together
```{r}
sv_combined <- bind_rows(sv_1, sv_2)
```
# Merge ct and sv to create df1 - containing all the brain scans for all the sites
```{r}
df1 <- merge(ct_combined, sv_combined) 
```
# Add demographic variables
```{r}
#Remove unnecessary columns in demographics 
demographics <- demographics[, !names(demographics) %in% c("record_id", "participant_number","death_01_dod", "residence_04_carehome", "site_name", "demog_08_hand", "demog_09_yearsofeducation","ethnicity")]

#Rename columns in demographics 
colnames(demographics)[which(names(demographics) == "demog_11_wbicno")] <- "RID" 
colnames(demographics)[which(names(demographics) == "demog_10_gender")] <- "sex" 
demographics$sex <- ifelse(demographics$sex == "Male", 1, 0) 

#Remove unecessary columns in sessions
sessions <- sessions[, !names(sessions) %in% c("record_id", "days_since_baseline", "scan_site", "eulerLeft", "eulerRight", "scan_date")]

#Rename columns in sessions 
colnames(sessions)[which(names(sessions) == "demog_11_wbicno")] <- "RID" 
colnames(sessions)[which(names(sessions) == "age_at_scan")] <- "age" 
                          
#Remove unnecessary columns in diagnosis 
diagnosis <- diagnosis[, !names(diagnosis) %in% c("record_id", "date_of_diagnosis", "symptom_onset")] 

#Rename columns in diagnosis 
colnames(diagnosis)[which(names(diagnosis) == "demog_11_wbicno")] <- "RID" 

#Remove columns in clinical scores 
 clinicalscores <- clinicalscores[, !names(clinicalscores) %in% c("record_id")]
 
# Rename demog_11_wbicno column to RID 
colnames(clinicalscores)[which(names(clinicalscores) == "demog_11_wbicno")] <- "RID" 
                              
```
# Create grouped_diagnosis file so you merge all the diagnosis into 1 
```{r}
diagnosis_amended <- diagnosis %>% group_by(RID) %>% summarise(diagnosis = paste(diagnosis, collapse = ', '), grouped_diagnosis = paste(grouped_diagnosis, collapse = ', ')) 

rm(ct_1_lh,ct_1_rh, ct_2_lh, ct_2_rh,sv_1,sv_2) #clean up dfs
```
#Merge everything 

```{r}
# Merge df1, diagnosis_amended, and demographics by RID 
df1_new <- merge(merge(df1, diagnosis_amended, by = "RID", all = TRUE), demographics, by = "RID", all = TRUE) 
# Merge with sessions by RID 
df1_new <- merge(df1_new, sessions, by = "RID", all = TRUE) 
# Print the merged data frame 
print(df1_new)
```
#RIDs to include and exclude 
#Create a table 
#Load table 
#generate code to get a list that is not part of your included columns 
#Remove them from your df1_new 

```{r}
subjects <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Other final files/Table for subjects.csv")

# Extract RIDs from each column
clinical_scores_rids <- na.omit(subjects$`Clinical scores`)
df1_rids <- na.omit(subjects$df1)
diagnosis_rids <- na.omit(subjects$diagnosis_amended)
sessions_rids <- na.omit(subjects$sessions)
demographics_rids <- na.omit(subjects$demographics)
# Find RIDs common across all specified columns
common_rids <- Reduce(intersect, list(clinical_scores_rids, df1_rids, diagnosis_rids, sessions_rids, demographics_rids))
# Print the common RIDs
print(common_rids)
# Ensure the "RIDs present in main 5" column exists and is initialised to NA
if(!"RIDs present in main 5" %in% colnames(subjects)) {
  subjects$`RIDs present in main 5` <- NA
}

# Store the common RIDs in the "RIDs present in main 5" column
subjects$`RIDs present in main 5` <- NA
subjects$`RIDs present in main 5`[1:length(common_rids)] <- common_rids


# Extract RIDs from each column
df1_rids <- na.omit(subjects$df1)
diagnosis_rids <- na.omit(subjects$diagnosis_amended)
sessions_rids <- na.omit(subjects$sessions)
demographics_rids <- na.omit(subjects$demographics)
clinical_scores_rids <- na.omit(subjects$`Clinical scores`)

# Find RIDs common across the specified columns (df1, demographics, diagnosis_amended, sessions)
common_rids_main4 <- Reduce(intersect, list(df1_rids, demographics_rids, diagnosis_rids, sessions_rids))

# Exclude RIDs present in Clinical scores
final_rids_main4 <- setdiff(common_rids_main4, clinical_scores_rids)

# Print the final RIDs for main 4
print(final_rids_main4)

# Ensure the "RIDs present in main 4" column exists and is initialized to NA
if(!"RIDs present in main 4" %in% colnames(subjects)) {
  subjects$`RIDs present in main 4` <- NA
}

# Store the final RIDs in the "RIDs present in main 4" column
subjects$`RIDs present in main 4` <- NA
subjects$`RIDs present in main 4`[1:length(final_rids_main4)] <- final_rids_main4

# Extract RIDs from each column and remove NAs
clinical_scores_rids <- na.omit(subjects$`Clinical scores`)
df1_rids <- na.omit(subjects$df1)
diagnosis_rids <- na.omit(subjects$diagnosis_amended)
sessions_rids <- na.omit(subjects$sessions)
demographics_rids <- na.omit(subjects$demographics)

# Find RIDs that satisfy combination 1
common_rids_combination1 <- Reduce(intersect, list(df1_rids, sessions_rids, clinical_scores_rids, diagnosis_rids, demographics_rids))

# Find RIDs that satisfy combination 2
common_rids_combination2 <- Reduce(intersect, list(df1_rids, sessions_rids, diagnosis_rids, demographics_rids))

# Combine all unique RIDs from the five columns
all_rids <- unique(c(clinical_scores_rids, df1_rids, diagnosis_rids, sessions_rids, demographics_rids))

# Combine RIDs from both combinations
valid_rids <- unique(c(common_rids_combination1, common_rids_combination2))

# Find RIDs that are not in the valid_rids
rids_to_be_excluded <- setdiff(all_rids, valid_rids)

# Print the RIDs to be excluded
print(rids_to_be_excluded)

# Ensure the "RIDs to be excluded" column exists and is initialized to NA
if(!"RIDs to be excluded" %in% colnames(subjects)) {
  subjects$`RIDs to be excluded` <- NA
}

# Store the RIDs to be excluded in the "RIDs to be excluded" column
subjects$`RIDs to be excluded` <- NA
subjects$`RIDs to be excluded`[1:length(rids_to_be_excluded)] <- rids_to_be_excluded
```
#Remove the RIDs from df1_new
```{r}
rids_to_remove <- c(25298, 31214, 31215, 31936, 33327, 33398, 33614, 34062, 34094, 34218, 34221, 34263, 34311, 34770, 34889, 35068, 35124, 35479, 35501, 36178, 36526, 36530, 36549, 36566,
36569, 36618, 36637, 36644, 36669, 35225, 35597, 35661, 35770, 35788, 35871, 35872,
35907, 35977, 36034, 36050, 36054, 36110, 36115, 36171, 36216, 36362, 36379, 36382,
36770, 36778, 36786, 36805, 36817, 36835, 36836, 36837, 37032, 32083, 33329, 33790,
34035, 34795, 34797, 35331, 36205, 36548, 36600, 36294, 36425, 36570, 36704, 36707,
36715, 36716, 36762, 36763, 36777, 36833, 36928, 36999, 37025, 37026)

df1_new <- df1_new[!df1_new$RID %in% rids_to_remove, ] 
```
#Add site data 
```{r}
# Add sitenum column based on site column
 df1_new$sitenum <- ifelse(df1_new$site == 1, 1, ifelse(df1_new$site == 2, 2, NA)) 

```
#Reorder columns in df1_new
```{r}
# Reorder columns 
df1_new <- df1_new[, c("RID", "diagnosis", "grouped_diagnosis", "sex", "site", "sitenum", "age", setdiff(names(df1_new), c("RID", "diagnosis", "grouped_diagnosis", "sex", "site", "sitenum", "age")))]
```
# Create df_a - Healthy and Functional/Attentional Memory Symptoms
```{r}
# Ensure there are no leading or trailing spaces in the 'grouped_diagnosis' column
df1_new$grouped_diagnosis <- trimws(df1_new$grouped_diagnosis)

# Filter rows containing either "Functional/Attentional Memory Symptoms" or "Healthy"
df_a <- df1_new[grepl("Functional/Attentional Memory Symptoms|Healthy", df1_new$grouped_diagnosis), ]

# Print the resulting dataframe to check if it worked
print(df_a)

df_a <- df_a %>%
  filter(!grepl("AD|MCI|Psychiatric_disorders|Other_cognitive_disorders", grouped_diagnosis))

```
# Create df_t 
```{r}

# Filter rows based on the condition on the grouped_diagnosis column
df_grouped <- df1_new %>%
  filter(str_detect(grouped_diagnosis, "AD|Non-AD Dementia|MCI"))

# Filter rows based on the condition on the diagnosis column
df_diagnosis <- df1_new %>%
  filter(str_detect(diagnosis, "F03X Unspecified dementia"))

# Combine the results
df_t <- bind_rows(df_grouped, df_diagnosis)

```
#----------------------------------------------
## - - - Match column names of  adaptation and test datasets  - - -
#----------------------------------------------
# Column checks for test data set
```{r}
df_t <- df_t %>% rename(sub_id = RID) # extract column names from data and also template cols_template <- as.data.frame(colnames(template)) 
cols_df_t <- as.data.frame(colnames(df_t)) # change location of some columns to match template df_t <- df_t %>% relocate(site, .after = sex) 

colnames(df_t) <- sub("G_and_S", "G&S", colnames(df_t)) 
df_t <- df_t %>% dplyr::rename("rh_G_Ins_lG&S_cent_ins_thickness" = "rh_G_Ins_lg_and_S_cent_ins_thickness") 
df_t <- df_t %>% dplyr::rename("lh_G_Ins_lG&S_cent_ins_thickness" = "lh_G_Ins_lg_and_S_cent_ins_thickness")

df_t <- df_t %>% relocate(sitenum, .after = site) 
df_t <- df_t %>% relocate(age, .before = sex) 
df_t <- df_t %>% relocate(sub_id, .before = age) # add in columns library(dplyr) 
df_t <- mutate(df_t, `lh_G&S_frontomargin_thickness.1` = 0) 
df_t <- df_t %>% relocate('lh_G&S_frontomargin_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_G&S_occipital_inf_thickness.1` = 0) 
df_t <- df_t %>% relocate('lh_G&S_occipital_inf_thickness.1', .before = 'rh_G&S_frontomargin_thickness')
 df_t <- mutate(df_t, `lh_G&S_paracentral_thickness.1` = 0) 
df_t <- df_t %>% relocate('lh_G&S_paracentral_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_G&S_subcentral_thickness.1` = 0) 
df_t <- df_t %>% relocate('lh_G&S_subcentral_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_G&S_transv_frontopol_thickness.1` = 0) 
df_t <- df_t %>% relocate('lh_G&S_transv_frontopol_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_G&S_cingul-Ant_thickness.1` = 0) 
df_t <- df_t %>% relocate('lh_G&S_cingul-Ant_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_G&S_cingul-Mid-Ant_thickness.1` = 0) 
df_t <- df_t %>% relocate('lh_G&S_cingul-Mid-Ant_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_G&S_cingul-Mid-Post_thickness.1` = 0) 
df_t <- df_t %>% relocate('lh_G&S_cingul-Mid-Post_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_G_Ins_lg&S_cent_ins_thickness` = 0) 
df_t <- df_t %>% relocate('lh_G_Ins_lg&S_cent_ins_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_S_intrapariet&P_trans_thickness` = 0) 
df_t <- df_t %>% relocate('lh_S_intrapariet&P_trans_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_S_oc_middle&Lunatus_thickness` = 0) 
df_t <- df_t %>% relocate('lh_S_oc_middle&Lunatus_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_S_oc_sup&transversal_thickness` = 0) 
df_t <- df_t %>% relocate('lh_S_oc_sup&transversal_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `lh_S_oc-temp_med&Lingual_thickness` = 0) 
df_t <- df_t %>% relocate('lh_S_oc-temp_med&Lingual_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_t <- mutate(df_t, `rh_G&S_frontomargin_thickness.1` = 0) 
df_t <- df_t %>% relocate('rh_G&S_frontomargin_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_G&S_occipital_inf_thickness.1` = 0) 
df_t <- df_t %>% relocate('rh_G&S_occipital_inf_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_G&S_paracentral_thickness.1` = 0) 
df_t <- df_t %>% relocate('rh_G&S_paracentral_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_G&S_subcentral_thickness.1` = 0) 
df_t <- df_t %>% relocate('rh_G&S_subcentral_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_G&S_transv_frontopol_thickness.1` = 0) 
df_t <- df_t %>% relocate('rh_G&S_transv_frontopol_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_G&S_cingul-Ant_thickness.1` = 0) 
df_t <- df_t %>% relocate('rh_G&S_cingul-Ant_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_G&S_cingul-Mid-Ant_thickness.1` = 0) 
df_t <- df_t %>% relocate('rh_G&S_cingul-Mid-Ant_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_G&S_cingul-Mid-Post_thickness.1` = 0) 
df_t <- df_t %>% relocate('rh_G&S_cingul-Mid-Post_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_G_Ins_lg&S_cent_ins_thickness` = 0) 
df_t <- df_t %>% relocate('rh_G_Ins_lg&S_cent_ins_thickness', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_S_intrapariet&P_trans_thickness` = 0) 
df_t <- df_t %>% relocate('rh_S_intrapariet&P_trans_thickness', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_S_oc_middle&Lunatus_thickness` = 0) 
df_t <- df_t %>% relocate('rh_S_oc_middle&Lunatus_thickness', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_S_oc_sup&transversal_thickness` = 0) 
df_t <- df_t %>% relocate('rh_S_oc_sup&transversal_thickness', .before = 'Left-Lateral-Ventricle') 
df_t <- mutate(df_t, `rh_S_oc-temp_med&Lingual_thickness` = 0) 
df_t <- df_t %>% relocate('rh_S_oc-temp_med&Lingual_thickness', .before = 'Left-Lateral-Ventricle') 

df_t <- df_t  %>% mutate(`BrainSegVolNotVentSurf` = 0)
df_t <- df_t  %>% mutate(`Left-Thalamus-Proper` = 0)
df_t <- df_t  %>% mutate(`Right-Thalamus-Proper` = 0)
df_t <- df_t  %>% mutate(`SupraTentorialVolNotVentVox` = 0)

df_t <- select(df_t, -BrainSegVolNotVent) 
df_t <- select(df_t, -BrainSegVolNotVent.y) 
df_t <- select(df_t, -eTIV.y)

colnames(df_t)[which(names(df_t) == "BrainSegVolNotVent.x")] <- "BrainSegVolNotVent"

colnames(df_t)[which(names(df_t) == "eTIV.x")] <- "eTIV"

df_t <- df_t %>% replace(is.na(.), 0)

``` 
## checks for labeling and order for template
```{r} 
# Automated check for same labeling 
template_cols <- colnames(template) # Extract the column names of original template 
df_t <- df_t[, template_cols] # Reorder the columns of df_t based on the col order of template 
columns_match <- identical(colnames(df_t), colnames(template)) # Double check if they have the same column names and order 
# Print the result 
if (columns_match) { print("Both data frames have the same column names and order.") } else { print("Column names or order are different between the data frames.") } 
```
#Column checks for adaptation data sets
```{r}
df_a <- df_a %>% rename(sub_id = RID) # extract column names from data and also template cols_template <- as.data.frame(colnames(template)) 
cols_df_a <- as.data.frame(colnames(df_a)) # change location of some columns to match template df_t <- df_t %>% relocate(site, .after = sex) 

colnames(df_a) <- sub("G_and_S", "G&S", colnames(df_a)) 
df_a <- df_a %>% dplyr::rename("rh_G_Ins_lG&S_cent_ins_thickness" = "rh_G_Ins_lg_and_S_cent_ins_thickness") 
df_a <- df_a %>% dplyr::rename("lh_G_Ins_lG&S_cent_ins_thickness" = "lh_G_Ins_lg_and_S_cent_ins_thickness")

df_a <- df_a %>% relocate(sitenum, .after = site) 
df_a <- df_a %>% relocate(age, .before = sex) 
df_a <- df_a %>% relocate(sub_id, .before = age) # add in columns library(dplyr) 
df_a <- mutate(df_a, `lh_G&S_frontomargin_thickness.1` = 0) 
df_a <- df_a %>% relocate('lh_G&S_frontomargin_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_G&S_occipital_inf_thickness.1` = 0) 
df_a <- df_a %>% relocate('lh_G&S_occipital_inf_thickness.1', .before = 'rh_G&S_frontomargin_thickness')
 df_a <- mutate(df_a, `lh_G&S_paracentral_thickness.1` = 0) 
df_a <- df_a %>% relocate('lh_G&S_paracentral_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_G&S_subcentral_thickness.1` = 0) 
df_a <- df_a %>% relocate('lh_G&S_subcentral_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_G&S_transv_frontopol_thickness.1` = 0) 
df_a <- df_a %>% relocate('lh_G&S_transv_frontopol_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_G&S_cingul-Ant_thickness.1` = 0) 
df_a <- df_a %>% relocate('lh_G&S_cingul-Ant_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_G&S_cingul-Mid-Ant_thickness.1` = 0) 
df_a <- df_a %>% relocate('lh_G&S_cingul-Mid-Ant_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_G&S_cingul-Mid-Post_thickness.1` = 0) 
df_a <- df_a %>% relocate('lh_G&S_cingul-Mid-Post_thickness.1', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_G_Ins_lg&S_cent_ins_thickness` = 0) 
df_a <- df_a %>% relocate('lh_G_Ins_lg&S_cent_ins_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_S_intrapariet&P_trans_thickness` = 0) 
df_a <- df_a %>% relocate('lh_S_intrapariet&P_trans_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_S_oc_middle&Lunatus_thickness` = 0) 
df_a <- df_a %>% relocate('lh_S_oc_middle&Lunatus_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_S_oc_sup&transversal_thickness` = 0) 
df_a <- df_a %>% relocate('lh_S_oc_sup&transversal_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `lh_S_oc-temp_med&Lingual_thickness` = 0) 
df_a <- df_a %>% relocate('lh_S_oc-temp_med&Lingual_thickness', .before = 'rh_G&S_frontomargin_thickness') 
df_a <- mutate(df_a, `rh_G&S_frontomargin_thickness.1` = 0) 
df_a <- df_a %>% relocate('rh_G&S_frontomargin_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_G&S_occipital_inf_thickness.1` = 0) 
df_a <- df_a %>% relocate('rh_G&S_occipital_inf_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_G&S_paracentral_thickness.1` = 0) 
df_a <- df_a %>% relocate('rh_G&S_paracentral_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_G&S_subcentral_thickness.1` = 0) 
df_a <- df_a %>% relocate('rh_G&S_subcentral_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_G&S_transv_frontopol_thickness.1` = 0) 
df_a <- df_a %>% relocate('rh_G&S_transv_frontopol_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_G&S_cingul-Ant_thickness.1` = 0) 
df_a <- df_a %>% relocate('rh_G&S_cingul-Ant_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_G&S_cingul-Mid-Ant_thickness.1` = 0) 
df_a <- df_a %>% relocate('rh_G&S_cingul-Mid-Ant_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_G&S_cingul-Mid-Post_thickness.1` = 0) 
df_a <- df_a %>% relocate('rh_G&S_cingul-Mid-Post_thickness.1', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_G_Ins_lg&S_cent_ins_thickness` = 0) 
df_a <- df_a %>% relocate('rh_G_Ins_lg&S_cent_ins_thickness', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_S_intrapariet&P_trans_thickness` = 0) 
df_a <- df_a %>% relocate('rh_S_intrapariet&P_trans_thickness', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_S_oc_middle&Lunatus_thickness` = 0) 
df_a <- df_a %>% relocate('rh_S_oc_middle&Lunatus_thickness', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_S_oc_sup&transversal_thickness` = 0) 
df_a <- df_a %>% relocate('rh_S_oc_sup&transversal_thickness', .before = 'Left-Lateral-Ventricle') 
df_a <- mutate(df_a, `rh_S_oc-temp_med&Lingual_thickness` = 0) 
df_a <- df_a %>% relocate('rh_S_oc-temp_med&Lingual_thickness', .before = 'Left-Lateral-Ventricle') 

df_a <- df_a  %>% mutate(`BrainSegVolNotVentSurf` = 0)
df_a <- df_a %>% mutate(`Left-Thalamus-Proper` = 0)
df_a <- df_a  %>% mutate(`Right-Thalamus-Proper` = 0)
df_a <- df_a  %>% mutate(`SupraTentorialVolNotVentVox` = 0)

df_a <- select(df_a, -BrainSegVolNotVent) 
df_a <- select(df_a, -BrainSegVolNotVent.y) 
df_a <- select(df_a, -eTIV.y)

colnames(df_a)[which(names(df_a) == "BrainSegVolNotVent.x")] <- "BrainSegVolNotVent"

colnames(df_a)[which(names(df_a) == "eTIV.x")] <- "eTIV"

df_a <- df_a %>% replace(is.na(.), 0)

```
## checks for labeling and order in adaptation data set
```{r}
# Automated check for same labeling 
template_cols <- colnames(template) # Extract the column names of original template 
df_a <- df_a[, template_cols] # Reorder the columns of df_a based on the col order of template 
columns_match <- identical(colnames(df_a), colnames(template)) # Double check if they have the same column names and order 
# Print the result 
if (columns_match) { print("Both data frames have the same column names and order.") } else { print("Column names or order are different between the data frames.") } 

```
#----------------------------------------------
## - - - Save variables  - - -
#----------------------------------------------
```{r}
# Check if there are any matches in sub_id between df_a and df_t
if (any(df_a$sub_id %in% df_t$sub_id)) {
  print("There are matches in sub_id between df_a and df_t.")
} else {
  print("There are no matches in sub_id between df_a and df_t.")
}

write.csv(df_a, "dfa_final.csv", row.names=FALSE)
write.csv(df_t, "dft_final.csv", row.names = FALSE)
```