---
title: "tOC Production"
Authors: Serena Verdi and James Cole 
Adapted for QMIN-MC data sample by Sneha Prasanna

This  script binerises the Z-scores produced by the normative modelling script into a total outlier count (tOC) metric for each participant, used for further analysis. The script also creates filtered data frames for available ACE-R, ACE-3 scores and Years of education. 

output: html_notebook
---
```{r}
library(cowplot)
library(data.table)
library(e1071)
library(dplyr)
library(ggplot2)
library(plot.matrix)
library(proxy)
library(psych)
library(tidyr)
library(stringr)
library(RPMG)
library(viridis)
library(effectsize)
library(corrplot)
library(ggseg)
library(ggsegExtra) ## you may need this for the proportional outlier maps depending on your R version
library(ggsegDesterieux) ## this is important for the proportional outlier maps 
library(ggpubr)
library(lme4)
library(lmtest)
library(arsenal)
library(lmerTest)
library(MuMIn)
library(effects)
library(ggeffects)
library(readr)
rm(list = ls())
```
# Clean files
```{r}
# z-scores generated from non-G NM google collab script (w/dummy rids to treat each brain scan individuals) 
df <- read.csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Z-scores/Z-scores final final Sneha.csv")

# Other phenotypic data I am interested in 
#1. Load Variables file.csv
#2. Load diagnosis_amended.csv
#3. Load clinical scores
#4. Merge clinical scores - DATE MATCH? 
#5. Merge diagnosis_amended + variables by RID --> variables1
#6. Merge #5variables1 with clinical scores - so relabel acertot37 to ACERTOTALSITE1, and ace3_35_atttot to ACETOTALSITE2. Then those RIDs who are from site 1 that do not have site 2, label as NA and vice versa. --> if NA does not work, just label it 0.

#Label the final file as additional_variables
variables <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Demographics/Variables.csv") 
diagnosis_amended <- read_csv("//Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Demographics/diagnosis_amended.csv")
clinicalscorescombined <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Demographics/Clinical Scores_inprogress.csv")

sessions <- read_csv("/Users/snehaprasanna/Desktop/Serena Verdi Project/QMIN/Demographics/Sessions.csv")
colnames(sessions)[which(names(sessions) == "demog_11_wbicno")] <- "sub_id" 
colnames(diagnosis_amended)[which(names(diagnosis_amended) == "RID")] <- "sub_id" 

#7. Check if the visit date falls in the range - MATCH DATE? Yes or No 
#8. If no or NA remove RID from merged1 and merged2

##2.Have clinic1 (with site 1 tests) and clinic2(with site 2 tests) 
#Columns in clinic 1 - sub_id, vis_01_dt, acer_37_acertot
#Columns in clinic 2 - sub_id, vis_01_dt, ace3_35_attot, ace_iii_complete 
clinic1 <- clinicalscorescombined[!is.na(clinicalscorescombined$acer_37_acertot), ] 
clinic1 <- clinicalscorescombined[!is.na(clinicalscorescombined$acer_41_langtot), ] 
clinic2 <- clinicalscorescombined[!is.na(clinicalscorescombined$ace3_34_ace3tot), ]
clinic2 <- clinicalscorescombined[!is.na(clinicalscorescombined$ace3_38_langtot), ]

#3. Load sessions file - scan_date col is important! Use grep function to retain the scan_date and sub_id column 
sessions <- sessions[grep("sub_id|scan_date",names(sessions))]

#4. Duplicate sessions file so that - sessions1 and sessions2
sessions1 <- sessions
sessions2 <- sessions

#5. Now merge the clinic1 with sessions1 (merged1), clinic2 with sessions2 (merged2)
ACER <- merge(clinic1, sessions1, by = "sub_id", all.x = TRUE)
ACE3 <- merge(clinic2, sessions2, by = "sub_id", all.x = TRUE)

ACER <- ACER [, !names(ACER) %in% c("ace_iii_complete", "ace3_35_atttot")]

ACE3 <- ACE3 [, !names(ACE3) %in% c("ace_iii_complete", "acer_37_acertot")]

ACER$vis_01_dt <- as.Date(ACER$vis_01_dt, format = "%d/%m/%Y")
ACE3$vis_01_dt <- as.Date(ACE3$vis_01_dt, format = "%d/%m/%Y")

ACER <- ACER %>% dplyr::rename("ACER_scores" = "acer_37_acertot")
ACER <- ACER %>% dplyr::rename("ACER_langtot" = "acer_41_langtot")
ACE3 <- ACE3 %>% dplyr::rename("ACE3_scores" = "ace3_34_ace3tot")
ACE3 <- ACE3 %>% dplyr::rename("ACE3_langtot" = "ace3_38_langtot")

ACER <- ACER %>% relocate("ACER_scores", .after = "scan_date") 
ACER <- ACER %>% relocate("ACER_langtot", .after = "ACER_scores") 
ACE3 <- ACE3 %>% relocate("ACE3_scores", .after = "scan_date") 
ACE3 <- ACE3 %>% relocate("ACE3_langtot", .after = "ACE3_scores") 

ACER <- ACER[!is.na(ACER$scan_date), ]
ACE3<- ACE3[!is.na(ACE3$scan_date), ]

  
```

#Clinical score date and brain scan dates were weeks apart for certain participants. Here a suitable range was determined using distribution maps and outliers to subset participants for ACE-III and ACE-R scores. The result was too wide for ACE-III as outliers in week ranges were from -95.1 (25% lower bound) weeks to 64.9 weeks (75% upper bound) from the brain scan, which may not be representative of the brain scan. ACE-III was more reasonable from -2.9 (25% lower bound) to 17.7 weeks, which was applied to both distributions to represent the participant's brain scan as closely as possible.  
```{r}
# Calculate the difference in days and update the "How many weeks?" column
ACER <- ACER %>%
  mutate('How many weeksR?' = as.numeric(difftime(scan_date, vis_01_dt, units = "weeks")))
ACE3 <- ACE3 %>%
  mutate('How many weeks3?' = as.numeric(difftime(scan_date, vis_01_dt, units = "weeks")))

ggplot(ACER, aes(x = `How many weeksR?`)) + 
  geom_density() + 
  ggtitle("Distribution of weeks for ACER scores") +
  xlab("Weeks Difference") +
  ylab("Density") +
  theme_minimal()

ggplot(ACE3, aes(x = `How many weeks3?`)) + 
  geom_density() + 
  ggtitle("Distribution of weeks for ACE3 scores") +
  xlab("Weeks Difference") +
  ylab("Density") +
  theme_minimal()
  
#ACE3
# Calculate Q1 (25th percentile) and Q3 (75th percentile)
Q1 <- quantile(ACE3$`How many weeks3?`, 0.25, na.rm = TRUE)
Q3 <- quantile(ACE3$`How many weeks3?`, 0.75, na.rm = TRUE)
# Calculate IQR
IQR <- Q3 - Q1
# Calculate lower and upper bounds for outliers
ACE3_lower_bound <- Q1 - 1.5 * IQR
ACE3_upper_bound <- Q3 + 1.5 * IQR
# Identify outliers
outliers <- ACE3$`How many weeks?`[ACE3$`How many weeks?` < ACE3_lower_bound | ACE3$`How many weeks3?` > ACE3_upper_bound]
# Print results
print(ACE3_lower_bound)
print(ACE3_upper_bound)
filtered_ACE3 <- ACE3[ACE3$`How many weeks3?` >= -2.5 & ACE3$`How many weeks3?` <= 17.5, ]
filtered_ACE3 <- filtered_ACE3[-grep("vis_01_dt|scan_date|acer_41_langtot",names(filtered_ACE3))]

#ACER
# Calculate Q1 (25th percentile) and Q3 (75th percentile)
Q1 <- quantile(ACER$`How many weeksR?`, 0.25, na.rm = TRUE)
Q3 <- quantile(ACER$`How many weeksR?`, 0.75, na.rm = TRUE)
# Calculate IQR
IQR <- Q3 - Q1
# Calculate lower and upper bounds for outliers
ACER_lower_bound <- Q1 - 1.5 * IQR
ACER_upper_bound <- Q3 + 1.5 * IQR
# Identify outliers
outliers <- ACER$`How many weeksR?`[ACER$`How many weeksR?` < ACER_lower_bound | ACER$`How many weeksR?` > ACER_upper_bound]
# Print results
print(ACER_lower_bound )
print(ACER_upper_bound)
filtered_ACER <- ACER[ACER$`How many weeksR?` >= -2.9 & ACER$`How many weeksR?` <= 17.7, ]
filtered_ACER <- filtered_ACER[-grep("vis_01_dt|scan_date|ace3_34_ace3tot|ace3_38_langtot",names(filtered_ACER))]
```

# Create df for ALL rois (ct and ca)
## Pull out all wanted data, so this cleans up all columns that we don't want
```{r}
df <- df[grep("sub_id|age|sex|Z_predict",names(df))] ## grep pulls out data, -grep removes data
```
### cortical thickness (ct) pull out & reformat
```{r}
## select ct
ct <- df[grep("lh|rh",names(df))]

## make Mean_Thickness variable
ct$Mean_Thickness <- rowMeans(ct[,c('rh_MeanThickness_thickness_Z_predict', 'lh_MeanThickness_thickness_Z_predict')], na.rm=TRUE)
ct <- ct %>% 
       select(-c("rh_MeanThickness_thickness_Z_predict", "lh_MeanThickness_thickness_Z_predict"))

## pull out other variables needed
df1 <- df[grep("sub_id|age|sex",names(df))] 
df1 <- cbind(df1,ct) ## bind to ct df

colnames(df1) <- sub("_Z_predict", " ", colnames(df1)) ##remove unwanted string
```
### subcortical volumes (ca) pull out & reformat to fit ggseg atlas for regional analysis
```{r}
df <- df[-grep("lh|rh|Gray|vessel|CSF|Vol",names(df))]##remove unwanted cols

colnames(df) <- sub("_Z_predict", " ", colnames(df))##remove unwanted string

# add in aseg data
data(aseg)
force(aseg)
aseg_labels <- as.data.frame(aseg) 


# rename cols 
df <- df %>% dplyr::rename("Left.Thalamus.Proper" = "Left.Thalamus.Proper ")
df <- df %>% dplyr::rename("Right.Thalamus.Proper" = "Right.Thalamus.Proper ")
df <- df %>% dplyr::rename("Left.Accumbens.area" = "Left.Accumbens.area ")
df <- df %>% dplyr::rename("Brain.Stem" = "Brain.Stem ")
df <- df %>% dplyr::rename("Right.Amygdala" = "Right.Amygdala ")
df <- df %>% dplyr::rename("Left.Pallidum" = "Left.Pallidum ")
df <- df %>% dplyr::rename("Left.choroid.plexus" = "Left.choroid.plexus ")
df <- df %>% dplyr::rename("Right.Inf.Lat.Vent" = "Right.Inf.Lat.Vent ")
df <- df %>% dplyr::rename("Left.VentralDC" = "Left.VentralDC ")
df <- df %>% dplyr::rename("Left.Caudate" = "Left.Caudate ")
df <- df %>% dplyr::rename("Right.Putamen" = "Right.Putamen ")
df <- df %>% dplyr::rename("Right.choroid.plexus" = "Right.choroid.plexus ")
df <- df %>% dplyr::rename("Right.Accumbens.area" = "Right.Accumbens.area ")
df <- df %>% dplyr::rename("X3rd.Ventricle" = "X3rd.Ventricle ")
df <- df %>% dplyr::rename("Right.Pallidum" = "Right.Pallidum ")
df <- df %>% dplyr::rename("Left.Putamen" = "Left.Putamen ")
df <- df %>% dplyr::rename("Left.Cerebellum.Cortex" = "Left.Cerebellum.Cortex ")
df <- df %>% dplyr::rename("Right.Hippocampus" = "Right.Hippocampus ")
df <- df %>% dplyr::rename("Right.Caudate" = "Right.Caudate ")
df <- df %>% dplyr::rename("Right.Cerebellum.Cortex" = "Right.Cerebellum.Cortex ")
df <- df %>% dplyr::rename("Left.Amygdala" = "Left.Amygdala ")
df <- df %>% dplyr::rename("Left.Hippocampus" = "Left.Hippocampus ")
df <- df %>% dplyr::rename("Right.Lateral.Ventricle" = "Right.Lateral.Ventricle ")
df <- df %>% dplyr::rename("X4th.Ventricle" = "X4th.Ventricle ")
df <- df %>% dplyr::rename("Left.Inf.Lat.Vent" = "Left.Inf.Lat.Vent ")
df <- df %>% dplyr::rename("Right.VentralDC" = "Right.VentralDC ")
df <- df %>% dplyr::rename("Left.Lateral.Ventricle" = "Left.Lateral.Ventricle ")
df <- df %>% dplyr::rename("Left.Cerebellum.White.Matter" = "Left.Cerebellum.White.Matter ")
df <- df %>% dplyr::rename("Right.Cerebellum.White.Matter" = "Right.Cerebellum.White.Matter ")
df <- df %>% dplyr::rename("subject_id" = "sub_id")

# invert ventricle Z-scores
df$X3rd.Ventricle <- df$X3rd.Ventricle*-1
df$Right.Lateral.Ventricle <- df$Right.Lateral.Ventricle*-1
df$Left.Lateral.Ventricle <- df$Left.Lateral.Ventricle*-1
df$X4th.Ventricle <- df$X4th.Ventricle*-1
df$Right.Inf.Lat.Vent <- df$Right.Inf.Lat.Vent*-1
df$Left.Inf.Lat.Vent <- df$Left.Inf.Lat.Vent*-1


# rename cols
df <- df %>% dplyr::rename("Left-Thalamus-Proper" = "Left.Thalamus.Proper")
df <- df %>% dplyr::rename("Right-Thalamus-Proper" = "Right.Thalamus.Proper")
df <- df %>% dplyr::rename("unknown1" = "Left.Accumbens.area")
df <- df %>% dplyr::rename("Brain-Stem" = "Brain.Stem")
df <- df %>% dplyr::rename("Right-Amygdala" = "Right.Amygdala")
df <- df %>% dplyr::rename("Left-Pallidum" = "Left.Pallidum")
df <- df %>% dplyr::rename("unknown2" = "Left.choroid.plexus")
df <- df %>% dplyr::rename("unknown3" = "Right.Inf.Lat.Vent")
df <- df %>% dplyr::rename("Left-VentralDC" = "Left.VentralDC")
df <- df %>% dplyr::rename("Left-Caudate" = "Left.Caudate")
df <- df %>% dplyr::rename("Right-Putamen" = "Right.Putamen")
df <- df %>% dplyr::rename("unknown4" = "Right.choroid.plexus")
df <- df %>% dplyr::rename("unknown5" = "Right.Accumbens.area")
df <- df %>% dplyr::rename("x3rd-ventricle" = "X3rd.Ventricle")
df <- df %>% dplyr::rename("Right-Pallidum" = "Right.Pallidum")
df <- df %>% dplyr::rename("Left-Putamen" = "Left.Putamen")
df <- df %>% dplyr::rename("unknown6" = "Left.Cerebellum.Cortex")
df <- df %>% dplyr::rename("Right-Hippocampus" = "Right.Hippocampus")
df <- df %>% dplyr::rename("Right-Caudate" = "Right.Caudate")
df <- df %>% dplyr::rename("unknown7" = "Right.Cerebellum.Cortex")
df <- df %>% dplyr::rename("Left-Amygdala" = "Left.Amygdala")
df <- df %>% dplyr::rename("Left-Hippocampus" = "Left.Hippocampus")
df <- df %>% dplyr::rename("Right-Lateral-Ventricle" = "Right.Lateral.Ventricle")
df <- df %>% dplyr::rename("x4th-ventricle" = "X4th.Ventricle")
df <- df %>% dplyr::rename("unknown8" = "Left.Inf.Lat.Vent")
df <- df %>% dplyr::rename("Right-VentralDC" = "Right.VentralDC")
df <- df %>% dplyr::rename("Left-Lateral-Ventricle" = "Left.Lateral.Ventricle")
df <- df %>% dplyr::rename("unknown9" = "Left.Cerebellum.White.Matter")
df <- df %>% dplyr::rename("right-cerebellum-white-matter" = "Right.Cerebellum.White.Matter")


## fyi missing data from atlas
#cc-anterior
#cc-central
#cc-mid-anterior
#cc-mid-posterior
#cc-posterior
#right-cerebellum-cortex


df <- df[-grep("unknown",names(df))] #remove unknown cols as we don't need them
df1 <- df1[grep("thickness|Thickness|diagnosis",names(df1))] #remove unknown cols 

rm(aseg_labels,aseg)
```
## merge ct and ca to make a clean df with just the neuroimaging data you want
```{r}
df <- cbind(df,df1)
```
# Merge other phenotypes
```{r}
variables <- variables %>% dplyr::rename("subject_id" = "sub_id")
df <-  merge(df ,variables, by="subject_id", all.x = TRUE) 

diagnosis_amended <- diagnosis_amended %>% dplyr::rename("subject_id" = "sub_id")
df <-  merge(df ,diagnosis_amended, by="subject_id", all.x = TRUE) 


filtered_ACER  <- filtered_ACER  %>% dplyr::rename("subject_id" = "sub_id")
df <-  merge(df, filtered_ACER , by="subject_id", all.x = TRUE) 


filtered_ACE3  <- filtered_ACE3  %>% dplyr::rename("subject_id" = "sub_id")
df <-  merge(df, filtered_ACE3 , by="subject_id", all.x = TRUE) 
df <- df %>% dplyr::rename("RID" = "subject_id")
```
# Reorder columns

```{r}
df <- df %>% relocate(ACER_scores, .after = sex)
df <- df %>% relocate('How many weeksR?', .after = ACER_scores)
df <- df %>% relocate(ACE3_scores, .after = 'How many weeksR?')
df <- df %>% relocate('How many weeks3?', .after = ACE3_scores)
df <- df %>% relocate("Years of education", .after = 'How many weeks3?')
df <- df %>% relocate("Ethnicity", .after = "Years of education")
df <- df %>% relocate("diagnosis", .after = sex)
df <- df %>% relocate("grouped_diagnosis", .after = diagnosis)
df <- df %>% relocate("ACER_langtot", .after = ACER_scores)
df <- df %>% relocate("ACE3_langtot", .after = ACE3_scores)
df <- df[-grep("days_since_baseline_scan.x|days_since_baseline_scan.y",names(df))]
```
# Data cleaning - ## Reformat categorical variables to factors
```{r}
# Replace "Alzheimer's disease" with "AD" in the diagnosis column
df$diagnosis <- gsub("Alzheimer's disease", "AD", df$diagnosis, fixed = TRUE)
# Replace "Mild Cognitive Impairment" with "MCI" in the diagnosis column
df$diagnosis <- gsub("Mild Cognitive Impairment", "MCI", df$diagnosis)
characters_to_remove <- c(
  "Anxiety,", "Corticobasal Syndrome,", "Stroke,", ", Cerebellar syndrome with cognitive impairment", "Uncertain,", "Traumatic brain injury,", ", Uncertain", "Unspecified dementia,", ", Functional/Attentional Memory Disorder", "Cerebral Amyloid Angiopathy", 
"progressive memory probs in context of epilepsy with atrophy and vascular burden,", ", Parkinson's disease", "Functional/Attentional Memory Disorder, ") 

# Create pattern by collapsing characters with | (OR operator) and including comma
pattern <- paste0(",?\\s*(", paste(characters_to_remove, collapse = "|"), ")")

# Remove specified characters from the diagnosis column
df$diagnosis <- gsub(pattern, "", df$diagnosis, ignore.case = TRUE)
df$diagnosis <- trimws(df$diagnosis)
# Ensure there are no leading/trailing spaces in the diagnosis column
df$diagnosis <- gsub("^\\s+|\\s+$", "", df$diagnosis)

# Replace words after "AD -" with an empty string
df$diagnosis <- gsub("AD - .*", "AD", df$diagnosis)
# Replace words after "AD -" with an empty string
df$diagnosis <- gsub("Frontotemporal dementia - .*", "Frontotemporal dementia", df$diagnosis)
# Replace ", Leucoencephalopathy" with an empty string
df$diagnosis <- gsub(", Leucoencephalopathy", "", df$diagnosis)
df$diagnosis <- gsub("Dementia with Lewy Bodies, AD", "Dementia with Lewy Bodies", df$diagnosis)
df$diagnosis <- gsub("MCI, Mixed dementia \\(AD and vascular dementia\\)", "Mixed dementia (AD and vascular dementia)", df$diagnosis)
df$diagnosis <- gsub("MCI, MCI", "MCI", df$diagnosis)
df$diagnosis <- gsub("MCI, AD", "AD", df$diagnosis)
```
## Assign sex labels 
```{r}
## 1 = male 0 = female is how it is labelled in the google collab script (when generating the NM)

df$sex <- gsub("1", "Male", df$sex)
df$sex <- gsub("0", "Female", df$sex)
df$sex <- factor(df$sex)

```

#Demographic table for all diagnoses (including disentangling the Other non-AD dementia group)
```{r}
summary_table <- df %>%
  group_by(diagnosis) %>%
  summarize(
    n = n(),
    mean_age = mean(age, na.rm = TRUE),
    sd_age = sd(age, na.rm = TRUE),
    min_age = min(age, na.rm = TRUE),
    max_age = max(age, na.rm = TRUE),
    mean_education = mean(`Years of education`, na.rm = TRUE),
    sd_education = sd(`Years of education`, na.rm = TRUE),
    min_education = min(`Years of education`, na.rm = TRUE),
    max_education = max(`Years of education`, na.rm = TRUE),
    mean_ace3 = mean(ACE3_scores, na.rm = TRUE),
    sd_ace3 = sd(ACE3_scores, na.rm = TRUE),
    min_ace3 = min(ACE3_scores, na.rm = TRUE),
    max_ace3 = max(ACE3_scores, na.rm = TRUE),
    mean_acer = mean(ACER_scores, na.rm = TRUE),
    sd_acer = sd(ACER_scores, na.rm = TRUE),
    min_acer = min(ACER_scores, na.rm = TRUE),
    max_acer = max(ACER_scores, na.rm = TRUE),
    mean_ace3_langtot = mean(ACE3_langtot, na.rm = TRUE),
    sd_ace3_langtot = sd(ACE3_langtot, na.rm = TRUE),
    min_ace3_langtot = min(ACE3_langtot, na.rm = TRUE),
    max_ace3_langtot = max(ACE3_langtot, na.rm = TRUE),
    mean_acer_langtot = mean(ACER_langtot, na.rm = TRUE),
    sd_acer_langtot = sd(ACER_langtot, na.rm = TRUE),
    min_acer_langtot = min(ACER_langtot, na.rm = TRUE),
    max_acer_langtot = max(ACER_langtot, na.rm = TRUE)
  ) %>%
  ungroup()

# Print the summary table
print(summary_table)


sex_ratio <- df %>%
  group_by(diagnosis) %>%
  summarize(
    male_count = sum(sex == "Male"),
    female_count = sum(sex == "Female")
  ) %>%
  mutate(sex_ratio = male_count / female_count)
print(sex_ratio)
```


```{r}
df$diagnosis <- gsub("Alcohol related dementia", "Other non-AD Dementias - Alcohol related dementia", df$diagnosis)
df$diagnosis <- gsub("Parkinson's disease dementia", "Other non-AD Dementias - Parkinson's disease dementia", df$diagnosis)
df$diagnosis <- gsub("Frontal dementia of vascular etiology", "Other non-AD Dementias - Frontal dementia of vascular etiology", df$diagnosis)
df$diagnosis <- gsub("Progressive Supranuclear Palsy", "Other non-AD Dementias - Progressive Supranuclear Palsy", df$diagnosis)
df$diagnosis <- gsub("Vascular dementia", "Other non-AD Dementias - Vascular dementia", df$diagnosis)
df$diagnosis <- gsub("F03X Unspecified dementia", "Other non-AD Dementias - F03X Unspecified dementia", df$diagnosis)
df$diagnosis <- gsub("Dementia with Lewy Bodies", "Other non-AD Dementias - Dementia with Lewy Bodies", df$diagnosis)

df <- df %>% relocate(diagnosis, .after = age) ##move to front to see the column easier
df <- df %>% relocate(grouped_diagnosis, .after = diagnosis)
df <- df[, !names(df) %in% c("grouped_diagnosis")]
df$diagnosis <- as.factor(df$diagnosis) ## factoring is useful for future stats
```

## Brief check of number of scans within each group n = diagnosis 
```{r}
# Replace specific strings with "Other non-AD Dementias" for table display
df$diagnosis <- gsub("Other non-AD Dementias - .*", "Other non-AD Dementias", df$diagnosis)
# Create the table with the modified diagnosis column
table(df$diagnosis)
table(df$sex) #split across gender
table(df$Ethnicity)
```
#----------------------------------------------
#Create total outlier score
#----------------------------------------------
#Remove mean thickness
```{r}
#df <- df[-grep("lh_MeanThickness_thickness|rh_MeanThickness_thickness",names(df))] ## you can keep this, but I preferred to not use it in my analysis and doesn't make sense having in the tOC
```
# Pick threshold
```{r}
# outlier_threshold <- -1.65 ## bottom 5%
outlier_threshold <- -1.96 ## bottom 2.5% ## I pick this to be consistent with other studies, and my prev work
# outlier_threshold <- -2.58 ## bottom 0.05%
```
# Binerise outliers and create total_outlier score ACROSS total ROIs (score per participant)
```{r}
df3 <- as.data.frame(ifelse(df[,13:181] < outlier_threshold,1,0)) ##just threshold these certain columnspr
df3 <- df3 %>% rename_all(paste0, "_bin") ## rename all binerised columns to have the suffix "_bin"
df$tOC <- rowSums(df3, na.rm=T) ## add up all of binerised outliers to make tOC
df <- cbind(df, df3)
rm(df3)
df <- df %>% relocate(tOC, .after = diagnosis) ## move tOC to front of df to visualize
df <- df[-grep("Mean_Thickness_bin",names(df))]
```
#Generate filtered data files to use further in the analysis
```{r}
# --------------------- ACE3 and ACER scores -----------------------------------
#Duplicate df to get an ACER file
df_ACER_filtered <- df
#Remove any NA values 
df_ACER_filtered <- df %>%
  mutate(ACER_scores = as.numeric(ACER_scores),
         `How many weeksR?` = as.numeric(`How many weeksR?`)) %>%
  filter(!is.na(ACER_scores) & !is.na(`How many weeksR?`))
df_ACER_filtered <- df_ACER_filtered %>% select(-`How many weeks3?`, -"ACE3_scores")

#Due to very small groups for some non-AD groups, they need to be grouped under "Other non-AD dementias" to ensure there are atleast 20 in each group for statistical analysis 
df_ACER_filtered$diagnosis <- gsub("Mixed dementia \\(AD and vascular dementia\\)", "Non-AD Dementias", df_ACER_filtered$diagnosis)
df_ACER_filtered$diagnosis <- gsub("Frontotemporal dementia", "Non-AD Dementias", df_ACER_filtered$diagnosis)
df_ACER_filtered$diagnosis <- gsub("Other non-AD Dementias", "Non-AD Dementias", df_ACER_filtered$diagnosis)

##Duplicate df to get an ACE3 file
df_ACE3_filtered <- df
df_ACE3_filtered <- df %>%
  mutate(ACE3_scores = as.numeric(ACE3_scores),
         `How many weeks3?` = as.numeric(`How many weeks3?`)) %>%
  filter(!is.na(ACE3_scores) & !is.na(`How many weeks3?`))
df_ACE3_filtered <- df_ACE3_filtered %>% select(-`How many weeksR?`, -"ACER_scores")

#Due to very small groups for some non-AD groups, they need to be grouped under "Other non-AD dementias" to ensure there are atleast 20 in each group for statistical analysis 
df_ACE3_filtered$diagnosis <- gsub("Mixed dementia \\(AD and vascular dementia\\)", "Non-AD Dementias", df_ACE3_filtered$diagnosis)
df_ACE3_filtered$diagnosis <- gsub("Frontotemporal dementia", "Non-AD Dementias", df_ACE3_filtered$diagnosis)
df_ACE3_filtered$diagnosis <- gsub("Other non-AD Dementias", "Non-AD Dementias", df_ACE3_filtered$diagnosis)

df_ACE3_filtered <- df_ACE3_filtered[-grep("ACER_langtot",names(df_ACE3_filtered))]
df_ACER_filtered <- df_ACER_filtered[-grep("ACE3_langtot",names(df_ACER_filtered))]
#------------------------Education Clean ---------------------------------------

df_edu_filtered <- df %>% filter(!is.na(`Years of education`))
```

#Export files
```{r}
write.csv(df, "toc_df.csv", row.names = FALSE)
write.csv(df_ACE3_filtered, "df_ACE3_filtered.csv", row.names = FALSE)
write.csv(df_ACER_filtered, "df_ACER_filtered.csv", row.names = FALSE)
write.csv(df_edu_filtered, "df_edu_filtered.csv", row.names = FALSE)
```



